### 2022-05-25 diagram_sub.tex
lots to commit

\begin{tikzpicture}[node distance=3.5cm,auto,>=latex',every node/.append style={align=center},int/.style={draw, minimum size=1cm},inverter/.style={rectangle,draw,inner sep=2pt,minimum size=6mm},]
    \node [int, ultra thick] (S)             {$S$};
    \node [int, right=of S, ultra thick] (E)             {$E$};
    \node [int, above right=of E, ultra thick] (Ia)             {$I_a$};
    \node [int, below right=of E, ultra thick] (Is)             {$I_s$};
    \node [int, right=of Ia, ultra thick] (R)             {$R$};
    \node [int, right=of Is, ultra thick] (D)             {$D$};
    \path[->, ultra thick] (S) edge node [above] {$\lambda(t)$} (E);
    \path[->, ultra thick] (E) edge node [sloped, above] {$p \mu$} (Ia);
    \path[->, ultra thick] (E) edge node [sloped, above] {$(1-p) \mu$} (Is);
    \path[->, ultra thick] (Ia) edge node [above] {$\gamma_a$} (R);
    \path[->, ultra thick] (Is) edge node [sloped, above] {$(1-f) \gamma_s$} (R);
    \path[->, ultra thick] (Is) edge node [above] {$f \gamma_s$} (D);
    \node [right=1.5cm of S, ultra thick] (Ts)             {};
    \path[->, ultra thick, dashed] (Ia.west) edge [out=180, in=90] node [sloped, above] {$\beta_a$} ([yshift=5mm]Ts.north);
    \path[->, ultra thick, dashed] (Is.west) edge [out=180, in=-90] node [sloped, above] {$(1-\delta) \beta_s$} (Ts.south);
    \node [right=8.5cm of E] (pic) {\includegraphics{figure_base.ggp.pdf}};
\end{tikzpicture}
\end{document}

>>>>

\begin{tikzpicture}[node distance=3.5cm,auto,>=latex',every node/.append style={align=center},int/.style={draw, minimum size=1cm},inverter/.style={rectangle,draw,inner sep=2pt,minimum size=6mm},]
    \node [int, ultra thick] (S)             {$S$};
    \node [int, right=of S, ultra thick] (E)             {$E$};
    \node [int, right=of E, ultra thick] (Ip)             {$Ip$};
    \node [int, above right=of Ip, ultra thick] (Ia)             {$I_a$};
    \node [int, below right=of Ip, ultra thick] (Is)             {$I_s$};
    \node [int, right=of Ia, ultra thick] (R)             {$R$};
    \node [int, right=of Is, ultra thick] (D)             {$D$};
    \path[->, ultra thick] (S) edge node [above] {$\lambda(t)$} (E);
    \path[->, ultra thick] (E) edge node [above] {$\sigma$} (Ip);
    \path[->, ultra thick] (Ip) edge node [sloped, above] {$p \mu$} (Ia);
    \path[->, ultra thick] (Ip) edge node [sloped, above] {$(1-p) \mu$} (Is);
    \path[->, ultra thick] (Ia) edge node [above] {$\gamma_a$} (R);
    \path[->, ultra thick] (Is) edge node [sloped, above] {$(1-f) \gamma_s$} (R);
    \path[->, ultra thick] (Is) edge node [above] {$f \gamma_s$} (D);
    \node [right=1.5cm of S, ultra thick] (Ts)             {};
    \path[->, ultra thick, dashed] (Ia.west) edge [out=180, in=90] node [sloped, above] {$\beta_a$} ([yshift=5mm]Ts.north);
    \path[->, ultra thick, dashed] (Ip.north) edge [out=90, in=90] node [sloped, above] {$\beta_p$} ([yshift=5mm]Ts.north);
    \path[->, ultra thick, dashed] (Is.west) edge [out=180, in=-90] node [sloped, above] {$(1-\delta) \beta_s$} (Ts.south);
    \node [below=15cm of S, anchor=west] (pic) {\includegraphics{figure_sub.ggp.pdf}};
\end{tikzpicture}
\end{document}

### 2022-05-25 main.tex
lots to commit

High values of $\delta$ may seem unrealistic---in practice, $\delta$ cannot be greater than the amouont of post-symptomatic transmission.
While several studies have estimated the proportion of pre-symptomatic transmission to be around 30\%--60\% for the SARS-CoV-2 wildtype strain, many of them were likely subject to

mitigation steps took place and before awareness of the
epidemic became widespread

\citep{he2020temporal}.

\cite{sender2021unmitigated} recently showed the proportion of pre-symptomatic transmission is likely lower than previously estimated

can be as low as 20\% (95\%CI: 6\%--32\%) in the absence of intervention measures, providing indirect support for the plausibility of high $\delta$ values.
In Supplementary Figure S1, we therefore consider a more realistic model which includes a presymptomatic stage before asymptomatic and symptomatic stages; and we assume that the behavioral effect

>>>>

High values of $\delta$ required for the nonlinear effects of asymptomaticity on deaths may seem unrealistic---in practice, $\delta$ cannot be greater than the amouont of post-symptomatic transmission.
While several studies have estimated the proportion of pre-symptomatic transmission to be around 30\%--60\% for the SARS-CoV-2 wildtype strain, many of them were likely subject to intervention and behavioral effects already as they were conducted after SARS-CoV-2 awareness became widespread \citep{he2020temporal}.
Instead, \cite{sender2021unmitigated} recently showed that the proportion of pre-symptomatic transmission can be as low as 20\% (95\%CI: 6\%--32\%) in the absence of intervention measures;
while this study provides indirect support for the feasibility of high $\delta$ values, it is still uncertain whether similar effects can be found in more realistic settings.

We therefore consider a series of mathematical models with increasing complexities to answer a more general question:
does intermediate amount of subclinical transmission lead to peak fatalities?

In Supplementary Figure S1, we therefore consider a more realistic model which includes a presymptomatic stage before asymptomatic and symptomatic stages; and we assume that the behavioral effect
